Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
camfort reference

\item We provide an implementation of our approach as an extension to
  CamFort, an open-source program analysis tool for Fortran;

@@

We evaluated our approach on top of CamFort, an open-source analysis
tool for Fortran programs, running the inference process over a corpus
of a million lines of Fortran code. We showed that our language is
capable of capturing many real-world uses of stencils and showed in a
case-study that it will detect (simulated) programmer errors.

>>>>

\item We provide an implementation of our approach as an extension to
  CamFort~\cite{camfort}, an open-source program analysis tool for Fortran;

@@

We evalauated our approach by extending CamFort, an open-source analysis
tool for Fortran programs~\cite{camfort}, running the inference process over a corpus
of a million lines of Fortran code. We showed that our language is
capable of capturing many real-world uses of stencils and showed in a
case-study that it will detect (simulated) programmer errors.
